---
title: "Figure 3"
output: html_document
---

```{r set-up, warning=FALSE, message=FALSE, results="hide"}
# Clear workspace
rm(list = ls())

# Load helper functions
source('helper_functions.R')

# Import libraries
packages = c("tidyr","dplyr","ggplot2","lme4","lmerTest","Hmisc","car","lmtest","Rarity","cowplot")
ipak(packages)

# Redo long calculations
redo_calc = 1;

## Load in Striatum Betas
featquery_res = read.csv("../data/roi_zstat.csv")
featquery_res$Sub = as.factor(featquery_res$Sub)

## Load in individual subject parameters
full.model.subj_parm = read.csv("../data/model_outputs/subject_parms/simpleFull_subjparms.csv")
```

### Plot trace

```{r}
# Read in posterior distribution of each parameter
d0 = read.csv("../data/model_outputs/trace_processed/simpleFull_trace_all.csv",header = F) 
colnames(d0) = c("a","t",
                       "exp_z_mot","exp_z_int",
                       "v_bias","v_stim","v_int")

d0$z_int = 1/(1+exp(-d0$exp_z_int))
d0$z_bias = d0$exp_z_mot

d0 = dplyr::select(d0, z_bias, v_bias)

# z_bias
z_95 = quantile(d0$z_bias,0.05)
z_diff = d0$z_bias
z_diff = as.data.frame(z_diff)

plot.z_diff = 
  ggplot(z_diff,aes(z_diff, y = ..scaled..)) +
  geom_density(alpha = 0.2, adjust = 5, size = 0) +
  geom_line(stat = "density", adjust = 5, size = 2.5) +
  #geom_vline(xintercept = z_95, size = 1) +
  geom_vline(xintercept = 0, size = 1, linetype="dashed") + 
  scale_colour_manual(values=myPalette) +
  #ggtitle("z bias") +
  theme(legend.position = "none",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.x  = element_text(size=14,color="black"),
        axis.text.y  = element_text(size=14,color="black"),
        axis.title.x = element_text(size=14),
        axis.title.y = element_text(size=14),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "bold", size = 15),
        plot.title = element_text(hjust = 0.5,face = "bold", size = (15))) +
  xlab("z_bias") + ylab("Density") +
  coord_cartesian(ylim=c(0, 1.1)) +
  scale_y_continuous(breaks=seq(0,1,0.25)) +
  scale_x_continuous(breaks=c(0, 0.1, 0.1))

# Shade area
plot_data <- as.data.frame(ggplot_build(plot.z_diff)$data[2])
plot.z_diff = plot.z_diff+ 
  geom_area(data = subset(plot_data, x > 0.001), aes(x=x, y=y-0.02), fill="grey", alpha = 0.8) + 
  geom_line(stat = "density", adjust = 5, size = 2.5)

# v_bias
v_95 = quantile(d0$v_bias,0.05)
v_diff = d0$v_bias
v_diff = as.data.frame(v_diff)

plot.v_diff = 
  ggplot(v_diff,aes(v_diff, y = ..scaled..)) +
  geom_density(alpha = 0.2, adjust = 5, size = 0) +
  geom_line(stat = "density", adjust = 5, size = 2.5) +
  # geom_vline(xintercept = v_95, size = 1) +
  geom_vline(xintercept = 0, size = 1, linetype="dashed") + 
  scale_colour_manual(values=myPalette) +
  #ggtitle("v bias") +
  theme(legend.position = "none",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.x  = element_text(size=14,color="black"),
        axis.text.y  = element_text(size=14,color="black"),
        axis.title.x = element_text(size=14),
        axis.title.y = element_text(size=14),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "bold", size = 15),
        plot.title = element_text(hjust = 0.5,face = "bold", size = (15))) +
  xlab("v_bias") + ylab("Density") +
  coord_cartesian(ylim=c(0, 1.1)) +
  scale_y_continuous(breaks=seq(0,1,0.25))

# Shade area
plot_data <- as.data.frame(ggplot_build(plot.v_diff)$data[2])
plot.v_diff = plot.v_diff+ 
  geom_area(data = subset(plot_data, x > 0.001), aes(x=x, y=y-0.02), fill="grey", alpha = 0.8) + 
  geom_line(stat = "density", adjust = 5, size = 2.5)

z_bias = mean(z_diff$z_diff < 0)
cat("P_z(S > F) = ", 1 - z_bias)

v_bias = mean(v_diff$v_diff < 0)
cat("P_v(S > F) = ", 1 - v_bias)
```


```{r fig.width = 3, fig.height = 3}
# Plot DIC
model.DIC = NULL
model.DIC$Model = c('z & v','z','v',"null")
model.DIC$DIC = c(12535,12619,12546,12735) # See HDDM Analysis 
model.DIC = as.data.frame(model.DIC)
model.DIC$Model = factor(model.DIC$Model, levels = c('z & v','z','v','null'))

DIC.fig = ggplot(model.DIC, aes(x = Model, y = DIC)) + 
  geom_bar(stat = "identity",width = 0.3) +
  coord_cartesian(ylim=c(12500, 12750)) +
    theme(axis.text.x  = element_text(size=13,color="black"),
        axis.text.y  = element_text(size=13,color="black"),
        axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=15),
        strip.text.x = element_text(face = "bold", size = 15))

```


```{r fig.width = 6, fig.height = 5}
plot_grid(DIC.fig, plot.z_diff, plot.v_diff, nrow = 2, labels = c('B','C','D'))
```

**B.** The z & v model has the lowest DIC score, indicating that it provides the best fit to participants’ data. See Table S1 for best-fit values and summary statistics of all model parameters. **C.** Posterior distribution of the starting point bias (zbias). Dashed line indicates 0 (no bias), More than 95% of the distribution was greater than 0, indicating credible evidence of a starting point bias. **D.** Posterior distribution of the drift bias (vbias). More than 95% of the distribution was greater than 0, indicating credible evidence of a drift bias. 
