---
title: "NAcc activity is associated with response bias"
output: html_document
---

```{r set-up, warning=FALSE, message=FALSE, results="hide"}
# Clear workspace
rm(list = ls())

# Load helper functions
source('helper_functions.R')

# Import libraries
packages = c("tidyr","dplyr","ggplot2","lme4","lmerTest","Hmisc","car","lmtest","Rarity","cowplot")
ipak(packages)

# Redo long calculations
redo_calc = 1;

## Load in Striatum Betas
featquery_res = read.csv("../data/roi_zstat.csv")
featquery_res$Sub = as.factor(featquery_res$Sub)

## Load in individual subject parameters
full.model.subj_parm = read.csv("../data/model_outputs/subject_parms/simpleFull_subjparms.csv")
```

### Load Data
```{r load-data}
# Read data
AllData = read.csv("../data/AllData.csv")

# Convert to factors
AllData$Sub = as.factor(AllData$Sub)
AllData$Pred = as.factor(AllData$Pred)
AllData$Want2See = as.factor(AllData$Want2See)
AllData$Con_Rev = factor(AllData$Con, levels = c('Coop','Comp'))
AllData_ValidTrials = filter(AllData, !(is.na(Choice)))

# Load psychometric results (see Fig. 2 code)
load("long_calc/ConditionxBet.Rda")
```

#### NAcc response to Motivation Consistent trials was higher in High Bias participants than Low Bias participants
```{r}
# Extract random slope of the interaction
intSlope = unlist(coef(res)$Sub$`ConCoop:Pred1`)

# Create datafrom for each subjec'ts bias, and order in descending order
SubBias_Striatum = as.data.frame(intSlope)
SubBias_Striatum$Sub = unique(AllData$Sub)

PE = select(featquery_res, Sub, accumbens) 

SubBias_Striatum = left_join(SubBias_Striatum ,PE) %>% 
  select(Sub,intSlope,accumbens)

# Median Split
SubBias_Striatum$medianBehav = SubBias_Striatum$intSlope > 
  median(SubBias_Striatum$intSlope)
SubBias_Striatum$medianBehav = factor(SubBias_Striatum$medianBehav, levels = c("TRUE", "FALSE"))
```

### NAcc response is associated with bias in starting point but not drift rate 
```{r fig.width = 9, fig.height = 3.5}
full.model.subj_parm$Sub = as.factor(full.model.subj_parm$Sub)
full.model.subj_parm = left_join(full.model.subj_parm,SubBias_Striatum)

# Calculate Neural Bias
NeuralBias = NULL
for (s in unique(AllData$Sub)){
  thisData = NULL
  this_res = lm(Prob ~ Cat_n + Con * Pred, data = subset(AllData_ValidTrials, Sub == s))
  this_coef = coef(this_res)["ConCoop:Pred1"]
  
  thisData$NeuralBias = this_coef
  NeuralBias = rbind(NeuralBias,thisData)
}
NeuralBias = as.numeric(NeuralBias)

# Add Neural Bias
full.model.subj_parm$NeuralBias = NeuralBias
```

```{r}
# Run GLM
lm.NAcc = summary(lm(scale(accumbens) ~ scale(z) + scale(drift_bias), full.model.subj_parm))
lm.NAcc
lm.NAcc.coef = lm.NAcc$coefficients

# Extract coefficents 
reg_coef = NULL
reg_coef$parm = c('z_bias','v_bias')
reg_coef$value = c(lm.NAcc.coef["scale(z)","Estimate"],lm.NAcc.coef["scale(drift_bias)","Estimate"])
reg_coef$SE = c(lm.NAcc.coef["scale(z)","Std. Error"],lm.NAcc.coef["scale(drift_bias)","Std. Error"])
reg_coef = as.data.frame(reg_coef)
reg_coef$parm = factor(reg_coef$parm, levels = c('z_bias','v_bias'))

# NAcc ~ Z bias + V Bias
plot.A = ggplot(reg_coef) +
  geom_bar(aes(x = parm, y = value), stat = "identity", width = 0.3) +
  geom_errorbar(aes(x = parm, ymin = value - SE, ymax = value + SE), stat = "identity", width = 0.1) +
      theme(axis.text.x  = element_text(size=10,color="black"),
        axis.text.y  = element_text(size=10,color="black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=10),
        strip.text.x = element_text(face = "bold", size = 10)) +
  ylab("Estimate") +
  coord_cartesian(ylim=c(-0.2, 0.82)) +
  scale_y_continuous(breaks = seq(-0.25, 0.75, 0.25))

```

```{r}
# Load NAcc Timecourse
NAcc_tc = read.csv('../data/NAcc_timecourse.csv')
NAcc_tc$Sub = as.factor(NAcc_tc$Sub)
NAcc_tc$MotCon = as.factor(NAcc_tc$MotCon)
NAcc_tc = left_join(NAcc_tc,SubBias_Striatum)

NAcc_tc_summary = group_by(NAcc_tc,MotCon,Time) %>%
  summarise(meanActivity = mean(Activity), se = sem(Activity))

# Convert TR to seconds
NAcc_tc_summary$Time = NAcc_tc_summary$Time * 2

# Plot NAcc Timecourse for High Bias subjects
plot.B = ggplot(subset(NAcc_tc_summary), 
                      aes(x=Time, y=meanActivity, linetype=MotCon)) +
  geom_line(size = 1) +
    theme(legend.position="none",
          axis.text.x  = element_text(size=10,color="black"),
      axis.text.y  = element_text(size=10,color="black"),
      axis.title.x = element_blank(),
      axis.title.y = element_text(size=10),
      strip.text.x = element_blank()) +
  geom_errorbar(aes(ymin=meanActivity-se, ymax=meanActivity+se), width=.3) +
  coord_cartesian(ylim=c(-0.12, 0.20)) +
  scale_x_continuous(breaks=seq(-8,8,2)) +
  xlab("Time (s)") + ylab("NAcc Activity")
```


```{r}
NAcc_tc_diff = 
  spread(NAcc_tc,MotCon,Activity) %>%
  mutate(diff = `1` - `2`)

NAcc_diff_summary = group_by(NAcc_tc_diff,Time) %>%
  summarise(meanDiff = mean(diff), se = sem(diff))

NAcc_diff_summary$Time = NAcc_diff_summary$Time * 2

plot.C = ggplot(NAcc_diff_summary, 
                      aes(x=Time, y=meanDiff)) +
  geom_line(size = 1) +
    theme(legend.position="none",
          axis.text.x  = element_text(size=10,color="black"),
      axis.text.y  = element_text(size=10,color="black"),
      axis.title.x = element_blank(),
      axis.title.y = element_text(size=10),
      strip.text.x = element_blank()) +
  geom_errorbar(aes(ymin=meanDiff-se, ymax=meanDiff+se), width=.3) +
  coord_cartesian(ylim=c(-0.12, 0.20)) +
  scale_x_continuous(breaks=seq(-8,8,2)) +
  xlab("Time (s)") + ylab("Difference")

```

```{r fig.width = 7.1, fig.height = 2}
plot_grid(plot.A, plot.B, plot.C, labels = c("A","B","C"), rel_widths = c(0.24, 0.38, 0.38), nrow = 1)
```

```{r}
t.test(Activity ~ MotCon, data = subset(NAcc_tc,Time == -4), paired = T)
```

**Figure 6.** NAcc activation is associated with response bias. Linear regression predicting participants’ NAcc response from the model estimates of their starting point bias (zbias) and drift bias (vbias). The regression coefficient for zbias was significant but that for vbias was not. **B.** NAcc timecourse time-locked to image onset, corrected for hemodynamic lag by shifting the BOLD data by 4 seconds. The trial starts with the “Waiting for Teammate/Opponent” screen at -6s. The teammate or opponent makes a bet at -4s, which remains on the screen for 4s. The image is presented at 0s and stays on screen for 4s. NAcc activity was significantly higher on Motivation Consistent trials than Motivation Inconsistent trials from 2s before image onset until image offset. Solid lines: Motivation Consistent trials. Dashed lines: Motivation Inconsistent trials. **C.**  Difference in activity between Motivation Consistent and Motivation Inconsistent trials peaked before image offset. *: p < 0.05, additional statistics reported in Table S2.


      