---
title: "Motivation biases face and scene selective neural activity during visual categorization."
output: html_document
---

```{r set-up, warning=FALSE, message=FALSE, results="hide"}
# Clear workspace
rm(list = ls())

# Load helper functions
source('helper_functions.R')

# Import libraries
packages = c("tidyr","dplyr","ggplot2","lme4","lmerTest","Hmisc","car","lmtest","Rarity","cowplot")
ipak(packages)

# Redo long calculations
redo_calc = 1;
```

#### Load Data
```{r load-data}
# Read data
AllData = read.csv("../data/AllData.csv")

# Convert to factors
AllData$Sub = as.factor(AllData$Sub)
AllData$Pred = as.factor(AllData$Pred)
AllData$Want2See = as.factor(AllData$Want2See)
AllData$Con_Rev = factor(AllData$Con, levels = c('Coop','Comp'))
AllData_ValidTrials = filter(AllData, !(is.na(Choice)))

# Load psychometric results (see Fig. 2 code)
load("long_calc/ConditionxBet.Rda")
```

####	Motivation biases category selective neural activity during visual categorization 
```{r}
## Median split participants
intSlope = unlist(coef(res)$Sub$`ConCoop:Pred1`)
SubBias = as.data.frame(intSlope)
SubBias$Sub = unique(AllData$Sub)
SubBias$medianBehave = SubBias$intSlope > median(SubBias$intSlope)

BiasedData =  subset(AllData_ValidTrials, Sub %in% SubBias$Sub[SubBias$medianBehav == "TRUE"])
UnbiasedData = subset(AllData_ValidTrials, Sub %in% SubBias$Sub[SubBias$medianBehav == "FALSE"])

if (redo_calc) {
  res.prob = lmer(Prob ~ Cat_n_z  + Con * Pred + (Con * Pred |Sub), AllData_ValidTrials)
  
  res.prob.bias = lmer(Prob ~ Cat_n_z  + Con * Pred + (Con * Pred |Sub), BiasedData)
  res.prob.unbias = lmer(Prob ~ Cat_n_z  + Con * Pred + (Con * Pred |Sub), UnbiasedData)

  save(res.prob, res.prob.bias, res.prob.unbias, file="long_calc/NeuralBias.Rda")
} else {
  load("long_calc/NeuralBias.Rda")
  }

AllData_ValidTrials = full_join(AllData_ValidTrials, SubBias)

res.int.con = lmer(Prob ~ Cat_n_z  + Con * Pred * intSlope + (Con * Pred|Sub), AllData_ValidTrials)
summary(res.int.con)

# High Bias participants
summary(res.prob.bias)

# Low Bias Participants
summary(res.prob.unbias)

# Bias Plot
plot.prob.bias = ggplot(BiasedData, aes(x=Cat_n,y=Prob,color = Pred)) +
  stat_summary(fun.y=mean,geom="point",size=2) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",width=1,
               fun.args = list(mult = 1)) + 
  theme(legend.position="none",
      panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.x  = element_text(size=13,color="black"),
        axis.text.y  = element_text(size=13,color="black"),
        axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=13),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "plain", size = 13)) +
  xlab("% Scene") + ylab("Classifier Prob(Scene)") +
  facet_grid(~Con_Rev, labeller=labeller(Con_Rev = c("Coop" = "Cooperation","Comp" = "Competition"))) +
  scale_colour_manual(values=myPalette) + 
  ggtitle("High Bias")

# Unbias plot
plot.prob.unbias = ggplot(UnbiasedData, aes(x=Cat_n,y=Prob,color = Pred)) +
  stat_summary(fun.y=mean,geom="point",size=2) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",width=1,
               fun.args = list(mult = 1)) + 
  theme(legend.position="none",
      panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.x  = element_text(size=13,color="black"),
        axis.text.y  = element_text(size=13,color="black"),
        axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=13),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "plain", size = 13)) +
  xlab("% Scene") + ylab("Classifier Prob(Scene)") + 
  facet_grid(~Con_Rev, labeller=labeller(Con_Rev = c("Coop" = "Cooperation","Comp" = "Competition"))) +
  scale_colour_manual(values=myPalette) + 
  ggtitle("Low Bias")

```

#### Neural bias was correlated with motivational bias
```{r fig.width = 9, fig.height=8}
NeuralBias = NULL
for (s in unique(AllData$Sub)){
  thisData = NULL
  this_res = lm(Prob ~ Cat_n + Con * Pred, data = subset(AllData_ValidTrials, Sub == s))
  this_coef = coef(this_res)["ConCoop:Pred1"]
  
  thisData$NeuralBias = this_coef
  NeuralBias = rbind(NeuralBias,thisData)
}
NeuralBias = as.numeric(NeuralBias)
cor.test(NeuralBias, intSlope)

correlationPlot = as.data.frame(cbind(NeuralBias, intSlope))

# Plot behavioral bias
plot.prob.behav = ggplot(data = correlationPlot, aes(x = NeuralBias, y = intSlope)) +
  geom_point() +
  geom_smooth(method='lm',se=FALSE, colour="black") +
    theme(legend.position="none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x  = element_text(size=13,color="black"),
        axis.text.y  = element_text(size=13,color="black"),
        axis.line = element_line(colour = "black"),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "bold"),
                plot.title = element_text(face = "plain", size = (15))) +
  coord_cartesian(ylim=c(-1.5, 5)) +
  ylab("Motivational Bias") + xlab("Neural Bias")

```

### Participants neural bias was associated with perceptual bias but not response bias
```{r fig.width = 9, fig.height=8}
# Load model parameters
full.model.subj_parm = read.csv("../data/model_outputs/subject_parms/simpleFull_subjparms.csv")
full.model.subj_parm$Sub = as.factor(full.model.subj_parm$Sub)
full.model.subj_parm = left_join(full.model.subj_parm,SubBias)
full.model.subj_parm$NeuralBias = NeuralBias

# Run GLM
lm.VVS = summary(lm(scale(NeuralBias) ~ scale(z) + scale(drift_bias), full.model.subj_parm))
lm.VVS
lm.VVS.coef = lm.VVS$coefficients

# Extract coefficents 
reg_coef = NULL
reg_coef$parm = c('z_bias','v_bias')
reg_coef$value = c(lm.VVS.coef["scale(z)","Estimate"],lm.VVS.coef["scale(drift_bias)","Estimate"])
reg_coef$SE = c(lm.VVS.coef["scale(z)","Std. Error"],lm.VVS.coef["scale(drift_bias)","Std. Error"])
reg_coef = as.data.frame(reg_coef)
reg_coef$parm = factor(reg_coef$parm, levels = c('z_bias','v_bias'))

# VVS ~ Z bias + V Bias
plot.VVS = ggplot(reg_coef) +
  geom_bar(aes(x = parm, y = value), stat = "identity", width = 0.2) +
  geom_errorbar(aes(x = parm, ymin = value - SE, ymax = value + SE), stat = "identity", width = 0.05) +
      theme(axis.text.x  = element_text(size=14,color="black"),
        axis.text.y  = element_text(size=14,color="black"),
        axis.title.y = element_text(size=14),
        strip.text.x = element_text(face = "bold", size = 14)) +
  ylab("Estimate") +
  xlab("NULL") + 
  coord_cartesian(ylim=c(-0.2, 0.8))

# Plot all
plot_grid(plot.prob.bias,plot.prob.unbias,plot.prob.behav, plot.VVS, labels = c('A','','B', 'C'), ncol = 2)
```

**Motivation biases face and scene selective neural activity during visual categorization.** **A.** Classifier probability that the presented image was a scene rather than a face based on the BOLD response in the ventral visual stream, separately for participants with high and low behavioral bias. Blue dots: teammate or opponent betting that the next image will be scene; Red dots: teammate or opponent betting that the next image will be a face. For High Bias participants, scene probability was higher when participants were motivated to see a scene (i.e. teammate bets scene or opponent bets face) than when participants were motivated to see a face (i.e. teammate bets face or opponent bets scene). There was no effect of motivation in Low Bias participants. **B.** The effect of motivation on classifier probability (Neural Bias) was correlated with the extent to which a participant was bias in his or her categorizations (Motivational Bias). **C.** Regression coefficients of the response bias (βz) and perceptual bias (βv) when both were entered into the same model to predict participants’ neural bias. Only the perceptual bias was significantly associated with participants’ neural bias. 

