---
title: "Figure S1"
output: html_document
---

This code plots drift rate separately for each level of % scene


```{r set-up, warning=FALSE, message=FALSE, results="hide"}
# Clear workspace
rm(list = ls())

# Load helper functions
source('helper_functions.R')

# Import libraries
packages = c("tidyr","dplyr","ggplot2","lme4","lmerTest","Hmisc","car","lmtest","Rarity","cowplot")
ipak(packages)

# Redo long calculations
redo_calc = 0;
```

### Load Data
```{r load-data}
# Read data
AllData = read.csv("../data/AllData.csv")

# Convert to factors
AllData$Sub = as.factor(AllData$Sub)
AllData$Pred = as.factor(AllData$Pred)
AllData$Want2See = as.factor(AllData$Want2See)
AllData$Con_Rev = factor(AllData$Con, levels = c('Coop','Comp'))

# Load psychometric results (see Fig. 2 code)
load("long_calc/ConditionxBet.Rda")

# Extract random slope of the interaction
intSlope = unlist(coef(res)$Sub$`ConCoop:Pred1`)

# Create datafrom for each subject's bias, and order in descending order
SubBias = as.data.frame(intSlope)
SubBias$Sub = unique(AllData$Sub)
SubBias = SubBias[order(-SubBias$intSlope), ]
```


```{r}
full.model.parm = read.csv("../data/model_outputs/subject_parms/SeparateDriftRate_parms.csv")

# Only keep paramters at the subject level 
full.model.subj_parm = filter(full.model.parm, grepl('subj', X)) %>% 
  select(X,mean)

# Only keep v parameter 
v_bias = filter(full.model.subj_parm, grepl('v_', X)) %>%
  separate("X",sep = c(1,7),into = c("parm","foo","foo2")) %>%
  separate("foo2", sep = "\\.", into = c("mot1","mot2","cat1","cat2","Sub")) %>%
  separate("cat2", into = c("cat2","foo2")) %>%
  unite(mot,c(mot1,mot2)) %>%
  unite(cat,c(cat1,cat2)) %>%
  unite(v_cond,c(mot,cat)) %>%
  select(Sub,mean,v_cond) %>%
  spread(v_cond,mean) %>%
  transmute(Sub = Sub,
    `v_-5_0` = `1_0_-5_0` - `-1_0_-5_0`,
         `v_-1_5` = `1_0_-1_5` - `-1_0_-1_5`,
         `v_-1_0` = `1_0_-1_0` - `-1_0_-1_0`,
         `v_-0_5` = `1_0_-0_5` - `-1_0_-0_5`,
         `v_0_0` = `1_0_0_0` - `-1_0_0_0`,
         `v_0_5` = `1_0_0_5` - `-1_0_0_5`,
         `v_1_0` = `1_0_1_0` - `-1_0_1_0`,
         `v_1_5` = `1_0_1_5` - `-1_0_1_5`,
         `v_5_0` = `1_0_5_0` - `-1_0_5_0`)

v_bias_tidy = v_bias %>%
  gather(type, value, c(2:10)) %>%
  separate(type, sep = "_", into = c("parm", "cat1", "cat2")) %>%
  unite(cat,c(cat1,cat2), sep = "")

v_bias_tidy$cat = as.numeric(v_bias_tidy$cat) + 50

summary(lmer(value ~ poly(cat,2) + (poly(cat,2)|Sub), data = v_bias_tidy))
summary(lmer(value ~ poly(cat,2) + (poly(cat,2)|Sub), data = subset(v_bias_tidy, (cat > 10) & (cat < 90))))

```

```{r fig.height= 4, fig.width = 8}
# Moderation
v_bias = filter(full.model.subj_parm, grepl('v_', X)) %>%
  separate("X",sep = c(1,7),into = c("parm","foo","foo2")) %>%
  separate("foo2", sep = "\\.", into = c("mot1","mot2","cat1","cat2","Sub")) %>%
  separate("cat2", into = c("cat2","foo2")) %>%
  dplyr::select(Sub,parm,mot1,cat1,cat2,mean) %>%
  unite(cat,c(cat1,cat2), sep = '')
  
v_bias$cat = as.numeric(v_bias$cat)
v_bias$Sub = factor(v_bias$Sub)
v_bias$mot1 = factor(v_bias$mot1)
v_bias = full_join(SubBias, v_bias)

v_bias$HighBias = v_bias$intSlope > median(v_bias$intSlope)
v_bias$medianBehav = ifelse(v_bias$HighBias, "HighBias", "LowBias")

summary(lmer(mean ~ mot1 + scale(cat) + (mot1 + scale(cat) |Sub), data = v_bias))

summary(lmer(mean ~ mot1 + intSlope*scale(cat) + (mot1 + intSlope*scale(cat) |Sub), data = v_bias))

summary(lmer(mean ~mot1 + cat + (mot1 + cat |Sub), data = subset(v_bias, medianBehav == "HighBias")))
summary(lmer(mean ~mot1 + cat + (mot1 + cat |Sub), data = subset(v_bias, medianBehav == "LowBias")))
summary(lmer(mean ~ intSlope*mot1 + cat + (intSlope*mot1 |Sub), data = v_bias))

ggplot() +
  stat_summary(data = v_bias, aes(x=cat,y=mean,color = mot1),
               fun.y=mean,geom="point",size=3, alpha = 0.70) +
  stat_summary(data = v_bias, aes(x=cat,y=mean,color = mot1),
               fun.data = mean_cl_normal, geom = "errorbar",width=1,
               fun.args = list(mult = 1)) + 
  theme(legend.position="none",
      panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.x  = element_text(size=13,color="black"),
        axis.text.y  = element_text(size=13,color="black"),
        axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=15),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "bold", size = 15)) +
  xlab("% Scene") + ylab("Drift Rate") +
  facet_grid(~medianBehav) + 
  #facet_grid(~medianBehav, labeller=labeller(Con_Rev = c("Coop" = "Cooperation","Comp" = "Competition"))) +
  scale_colour_manual(values=myPalette)

```

**Motivational bias was not related to perceptual sensitivity. A.** Schematic illustration of relationship between % scene and drift rate for an individual with low perceptual sensitivity (left) and an individual with high sensitivity (right). For an individual with low perceptual sensitivity, the drift rate for face majority images (i.e. % scene < 50%) will be less negative, while the drift rate for scene majority images (i.e. % scene > 50%) will be less positive, resulting in an overall weaker relationship between % scene and drift rate. **B.** Relationship between % scene and drift rate, separately for High Bias and Low Bias participants. The two groups differed only in the effect of motivation on the drift rate (i.e. vertical distance between blue and red dots), and not in relationship between % scene and drift rate (i.e. average slope). Blue: drift rate when participants were motivated to see more scene. Red: drift rate when participants were motivated to see more face. Error bars indicate across-subject SEM.
