---
title: "Low Bias NAcc Timecourse"
output: html_document
---

```{r set-up, warning=FALSE, message=FALSE, results="hide"}
# Clear workspace
rm(list = ls())

# Load helper functions
source('helper_functions.R')

# Import libraries
packages = c("tidyr","dplyr","ggplot2","lme4","lmerTest","Hmisc","car","lmtest","Rarity","cowplot")
ipak(packages)

# Redo long calculations
redo_calc = 0;
```

```{r load-data}
# Read data
AllData = read.csv("../data/AllData.csv")

# Convert to factors
AllData$Sub = as.factor(AllData$Sub)
AllData$Pred = as.factor(AllData$Pred)
AllData$Want2See = as.factor(AllData$Want2See)
AllData$Con_Rev = factor(AllData$Con, levels = c('Coop','Comp'))

# Load stats
load("long_calc/ConditionxBet.Rda")
```

```{r warning=F}
# Extract random slope of the interaction
intSlope = unlist(coef(res)$Sub$`ConCoop:Pred1`)

# Create datafrom for each subjec'ts bias, and order in descending order
SubBias = as.data.frame(intSlope)
SubBias$Sub = unique(AllData$Sub)
SubBias = SubBias[order(-SubBias$intSlope),]

SubBias$medianBehav = SubBias$intSlope > median(SubBias$intSlope)
```

```{r fig.width = 8, fig.height = 4}
# Read NAcc time course
NAcc_tc = read.csv('../data/NAcc_timecourse.csv')
NAcc_tc$Sub = as.factor(NAcc_tc$Sub)
NAcc_tc$MotCon = as.factor(NAcc_tc$MotCon)
NAcc_tc = left_join(NAcc_tc,SubBias)

NAcc_tc_summary = group_by(NAcc_tc,MotCon,Time,medianBehav) %>%
  summarise(meanActivity = mean(Activity), se = sem(Activity))

NAcc_tc_summary$Time = NAcc_tc_summary$Time * 2

ggplot(subset(NAcc_tc_summary, medianBehav == FALSE), 
                      aes(x=Time, y=meanActivity, linetype=MotCon)) +
  geom_line(size = 1.5) +
    theme(legend.position="none",
          axis.text.x  = element_text(size=14,color="black"),
      axis.text.y  = element_text(size=14,color="black"),
      axis.title.x = element_text(size=14),
      axis.title.y = element_text(size=14),
      strip.text.x = element_blank()) +
  geom_errorbar(aes(ymin=meanActivity-se, ymax=meanActivity+se), width=.3) +
  coord_cartesian(ylim=c(-0.12, 0.20)) +
  scale_x_continuous(breaks=seq(-8,8,2)) +
  xlab("Time (s)") + ylab("NAcc Activity (z)")

```

**NAcc activity was not significantly different between Motivation Consistent trials and Motivation Inconsistent trials for Low Bias participants**. NAcc timecourse of Low Bias participants time-locked to image onset, corrected for hemodynamic lag by shifting the BOLD data by 4 seconds. The trial starts with the “Waiting for Teammate/Opponent” screen at -6s. The teammate or opponent makes a bet at -4s, which remains on the screen for 4s. The image is presented at 0s and stays on screen for 4s. Solid lines: Motivation Consistent trials. Dashed lines: Motivation Inconsistent trials.

