---
title: "Individual subject fits"
output: html_document
---
```{r set-up, warning=FALSE, message=FALSE, results="hide"}
# Clear workspace
rm(list = ls())

# Load helper functions
source('helper_functions.R')

# Import libraries
packages = c("tidyr","dplyr","ggplot2","lme4","lmerTest","Hmisc","car","lmtest","Rarity","cowplot")
ipak(packages)

# Redo long calculations
redo_calc = 1;
```

### Load Data
```{r load-data}
# Read data
AllData = read.csv("../data/AllData.csv")

# Convert to factors
AllData$Sub = as.factor(AllData$Sub)
AllData$Pred = as.factor(AllData$Pred)
AllData$Want2See = as.factor(AllData$Want2See)
AllData$Con_Rev = factor(AllData$Con, levels = c('Coop','Comp'))
```


```{r fig.width = 10, fig.height = 8}
# Plot RT
AllData_ValidTrials = filter(AllData, !(is.na(Choice)))
AllData_ValidTrials$RT_Rev = as.numeric(as.character(AllData_ValidTrials$RT))
AllData_ValidTrials$RT_Rev[AllData_ValidTrials$Choice < 0.5] = AllData_ValidTrials$RT_Rev[AllData_ValidTrials$Choice < 0.5] * - 1
AllData_ValidTrials$Want2See = ifelse(AllData_ValidTrials$Want2See == "0", "MotFace", "MotScene")
AllData_ValidTrials$Want2See = factor(AllData_ValidTrials$Want2See)


PPC = read.csv("https://www.dropbox.com/s/8ggv6iwkv1qs9fo/simpleFull_ppc.csv?dl=1", header = F)

# Wrangle data
colnames(PPC) = c("index","p_rt","p_response","Sub","stim","response","rt","condition","mot_con")
PPC$Sub = as.factor(PPC$Sub)
PPC$p_response = ifelse(PPC$p_rt > 0, 1, 0)
PPC$RT_Rev = PPC$p_rt

PPC$Want2See = ifelse(PPC$condition < 0, "MotFace", "MotScene")
PPC$Want2See = factor(PPC$Want2See)

# Recode subject
AllSub = NULL
AllSub$Sub = unique(AllData_ValidTrials$Sub)
AllSub$SubID = c(1:30)
AllSub = as.data.frame(AllSub)
AllSub$SubID = factor(AllSub$SubID)

AllData_ValidTrials = left_join(AllData_ValidTrials,AllSub)
PPC = left_join(PPC,AllSub)

PPC_timebound = PPC[(abs(PPC$p_rt) < 4) & (abs(PPC$p_rt) > 0.3),]
PPC_positive = PPC_timebound[PPC_timebound$p_rt > 0,]
PPC_negative = PPC_timebound[PPC_timebound$p_rt < 0,]

ggplot() + 
  geom_histogram(data = AllData_ValidTrials,  aes(x = RT_Rev, y = ..ncount..)) +
  geom_line(data = PPC_timebound, stat = "density", aes(x = RT_Rev, y = ..scaled..), size = 1.5, color='steelblue', alpha = 0.6) +
  xlab("RT(s)") + ylab("Probability") +
  theme(axis.text.y  = element_blank()) +
  facet_wrap(~ SubID + Want2See, nrow = 6) +
  coord_cartesian(xlim = c(-4.1, 4.1))
```
**Observed and predicted choice and RT distribution of each participant.** RTs for face responses were sign-flipped for illustration purposes. For each participant, we plot the RT distributions for face (negative RTs) and scene responses (positive RTs) separately for when the participant was motivated to see more face (MotFace) and for when the participant was motivated to see more scene (MotScene). Blue line indicates model-predicted choice and RT distributions.