<style>div.comment {color:blue}</style>
---
title: "Motivation biases category selective neural activity during visual categorization"
output: html_document
---

```{r set-up, warning=FALSE, message=FALSE, results="hide"}
# Clear workspace
rm(list = ls())

# Load helper functions
source('helper_functions.R')

# Import libraries
packages = c("tidyr","dplyr","ggplot2","lme4","lmerTest","Hmisc","car","lmtest","Rarity","cowplot")
ipak(packages)

# Redo long calculations
redo_calc = 1;
```

```{r load-data}
# Read data
AllData = read.csv("../data/AllData.csv")

# Convert to factors
AllData$Sub = as.factor(AllData$Sub)
AllData$Pred = as.factor(AllData$Pred)
AllData$Want2See = as.factor(AllData$Want2See)
AllData$Con_Rev = factor(AllData$Con, levels = c('Coop','Comp'))
AllData_ValidTrials = filter(AllData, !(is.na(Choice)))

# Load stats
load("long_calc/ConditionxBet.Rda")
```

```{r fig.height= 5, fig.width = 8}
res.prob = lmer(Prob ~ Cat_n_z  + Con * Pred + (Con * Pred |Sub), AllData_ValidTrials)
summary(res.prob)

ggplot(AllData_ValidTrials, aes(x=Cat_n,y=Prob,color = Pred)) +
  stat_summary(fun.y=mean,geom="point",size=2) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",width=1,
               fun.args = list(mult = 1)) + 
  theme(legend.position="none",
      panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.x  = element_text(size=13,color="black"),
        axis.text.y  = element_text(size=13,color="black"),
        axis.title.x = element_text(size=15),
        axis.title.y = element_text(size=13),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "plain", size = 13)) +
  xlab("% Scene") + ylab("Classifier Prob(Scene)") +
  facet_grid(~Con_Rev, labeller=labeller(Con_Rev = c("Coop" = "Cooperation","Comp" = "Competition"))) +
  scale_colour_manual(values=myPalette)
```

**Motivation biases face and scene selective neural activity during visual categorization.** Classifier probability that the presented image was a scene rather than a face based on the BOLD response in the ventral visual stream. Red dots: teammate or opponent betting that the next image will be a face. Scene probability was higher when participants were motivated to see a scene (i.e. teammate bets scene or opponent bets face) than when participants were motivated to see a face (i.e. teammate bets face or opponent bets scene), β = 0.03, SE = 0.02, t(4756) = 2.05, p = 0.040. 
